Check matrix correlations

### 2019-04-17 Analysis/04-CheckMatrixCorrelation.Rmd
Updated character correlations

```{r, echo = FALSE}
caption <- paste0("Pairwise Wilcoxon test and Bhattacharrya Coefficients for the difference in",
  " proportion of character replacement for the different scenarios, number of taxa and characters.")
kable(combined_results, digits = 3, caption = caption)
```

@@

```{r}
## Get character difference change value
get.char.replace <- function(chain) {
    ## Get the duplicates
    all_duplicates <- lapply(chain$changes, function(X) return(length(unique(X[,2]))))
    ## Make them proportional
    return(mapply(function(x,y) return(x/y), all_duplicates, as.list(c(100, 350, 1000)),
                 SIMPLIFY = FALSE))

}
## Get the number of duplicated characters
parameters_duplicates <- lapply(parameters, lapply, lapply, get.char.replace)
```

@@

```{r, fig.height = 18, fig.width = 6}
## Extract the results for each type of scenarios
duplicates_maxi <- lapply(parameters_duplicates, lapply, extract.results, what = "maxi")
duplciates_mini <- lapply(parameters_duplicates, lapply, extract.results, what = "mini")
duplicates_rand <- lapply(parameters_duplicates, lapply, extract.results, what = "rand")

## overal_range (for plotting)
overal_range <- range(c(unlist(duplicates_maxi), unlist(duplciates_mini), unlist(duplicates_rand)))

## Plotting the different proportion results
par(mfrow = c(3,1))
plot.proportions(duplicates_maxi, ylim = overal_range, main = "Maximised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
plot.proportions(duplciates_mini, ylim = overal_range, main = "Minimised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
plot.proportions(duplicates_rand, ylim = overal_range, main = "Randomised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
```

@@

```{r, fig.height = 18, fig.width = 6, eval = TRUE, echo = FALSE}
pdf("../Writing/Figures/Difference_change_maxi.pdf", width = 6, height = 6)
plot.proportions(differences_maxi, ylim = overal_range, main = "Maximised", leg.pos = "bottomleft")
pdf("../Writing/Figures/Difference_change_mini.pdf", width = 6, height = 6)
plot.proportions(differences_mini, ylim = overal_range, main = "Minimised", leg.pos = "topleft")
pdf("../Writing/Figures/Difference_change_rand.pdf", width = 6, height = 6)
plot.proportions(differences_rand, ylim = overal_range, main = "Randomised", leg.pos = "topleft"))
```

@@

@@

@@

```{r, echo = FALSE}
caption <- paste0("Pairwise Wilcoxon test and Bhattacharrya Coefficients for the difference in",
  " proportion of character replacement for the different scenarios, number of taxa and characters.")
kable(combined_results, digits = 3, caption = caption)
```

>>>>

```{r, echo = FALSE}
caption <- paste0("Pairwise Wilcoxon test and Bhattacharrya Coefficients for the differences in",
  "character difference for the different scenarios, number of taxa and characters.")
kable(combined_results, digits = 3, caption = caption)
```

@@

```{r}
## Get character difference change value
get.char.replace <- function(chain) {
    return(lapply(chain$changes, function(X) return(length(unique(X[,2])))))
}
## Get the number of duplicated characters
parameters_duplicates <- lapply(parameters, lapply, lapply, get.char.replace)
```

@@

```{r, fig.height = 18, fig.width = 6}
## Make the characters proportional
make.prop <- function(list) {
    return(mapply(function(x,y) return(x/y), list, as.list(c(100, 350, 1000)),
                 SIMPLIFY = FALSE))
}

## Extract the results for each type of scenarios
duplicates_maxi <- lapply(lapply(parameters_duplicates, lapply, extract.results, what = "maxi"),
                        make.prop)
duplicates_mini <- lapply(lapply(parameters_duplicates, lapply, extract.results, what = "mini"),
                        make.prop)
duplicates_rand <- lapply(lapply(parameters_duplicates, lapply, extract.results, what = "rand"),
                        make.prop)

## overal_range (for plotting)
overal_range <- c(0,1)

## Plotting the different proportion results
par(mfrow = c(3,1))
plot.proportions(duplicates_maxi, ylim = overal_range, main = "Maximised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
plot.proportions(duplicates_mini, ylim = overal_range, main = "Minimised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
plot.proportions(duplicates_rand, ylim = overal_range, main = "Randomised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
```

@@

```{r, fig.height = 18, fig.width = 6, eval = TRUE, echo = FALSE}
pdf("../Writing/Figures/Proportion_duplicated_maxi.pdf", width = 6, height = 6)
plot.proportions(duplicates_maxi, ylim = overal_range, main = "Maximised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
pdf("../Writing/Figures/Proportion_duplicated_mini.pdf", width = 6, height = 6)
plot.proportions(duplicates_mini, ylim = overal_range, main = "Minimised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
pdf("../Writing/Figures/Proportion_duplicated_rand.pdf", width = 6, height = 6)
plot.proportions(duplicates_rand, ylim = overal_range, main = "Randomised", leg.pos = "topleft",
    ylab = "Proportion of duplicated characters")
```

@@

```{r}
## Generating the nested tables
table_maxi <- convert.df(duplicates_maxi)
table_mini <- convert.df(duplicates_mini)
table_rand <- convert.df(duplicates_rand)

@@

```{r}
## Running the wilcox tests for each pooled factor
wilcox_scen <- pair.test(all_results, factor = "scenario", wilcox.test)
wilcox_taxa <- pair.test(all_results, factor = "taxa", wilcox.test)
wilcox_char <- pair.test(all_results, factor = "characters", wilcox.test)

@@

```{r, echo = FALSE}
caption <- paste0("Pairwise Wilcoxon test and Bhattacharrya Coefficients for the difference in",
  " proportion of character duplicated for the different scenarios, number of taxa and characters.")
kable(combined_results, digits = 3, caption = caption)
```

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
library(xtable)
source("../Functions/make.xtable.R")
make.xtable(combined_results, caption = caption, label = "Tab_proportion_duplicated",
            path = "../Writing/Tables/", include.rownames = TRUE)
```
